### 2025-07-11 README.Rmd
reorganise folders
Ms: add Jokura et al Zenodo ref, update Readme.Rmd

# About the project: 
- this is a repository of an R project containing code and source data for the ctenophore apical organ connectome paper. Contributed by [Jékely lab](https://www.cos.uni-heidelberg.de/en/research-groups/gaspar-jekely).

@@

> Authors, (YYYY). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>

Our pre-print is online here:

> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

Please cite this compendium as:

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

  - [:file\_folder: text](/text/Manuscript.qmd): Quarto source document
    for manuscript. Includes text, references and inserts the latest version of the figures from the /figures folder. 
There is also a rendered html version,
    `Manuscript.html`, suitable for reading.

  - [:file\_folder: data](analysis/data): Data used in the analysis.
  - [:file\_folder: data](analysis/scripts): scripts used in the analysis.
  - [:file\_folder: figures](manuscript/figures): Plots and other
    illustrations
  - [:file\_folder:
    supplements](manuscript/supplements):
    Supplementary materials including notes and other documents
    prepared and collected during the analysis.
  - [:file\_folder:
    source_data](/manuscript/source_data):
    Source data files associated with each figure containing all data points that have been plotted in the figure.

>>>>

# About the project: 
- this is a repository of an R project containing code and source data for the paper **Neural Connectome of the Ctenophore Statocyst**. Contributed by [Jékely lab](https://www.cos.uni-heidelberg.de/en/research-groups/gaspar-jekely).

@@

*Neural Connectome of the Ctenophore Statocyst*\
Kei Jokura, Sanja Jasek, Lara Niederhaus, Pawel Burkhardt, Gáspár Jékely\
bioRxiv 2025.06.26.661250; doi: <https://doi.org/10.1101/2025.06.26.661250>

@@

Please cite the permanend Zenodo record for this compendium as:

Jokura, K., Jasek, S., & Jékely, G. (2025). \
Code documentation for Neural Connectome of the Ctenophore Statocyst (v1.0). Zenodo.\
https://doi.org/10.5281/zenodo.15861953

@@

  - [:file\_folder: manuscript](/manuscript/Manuscript.qmd): Quarto source document
    for manuscript. Includes text, references and inserts the latest version of the figures from the /figures folder. 
There is also a rendered html version,
    `Manuscript.html`, suitable for reading.

  - [:file\_folder: data](analysis/data): Data used in the analysis.
  - [:file\_folder: scripts](analysis/scripts): scripts used in the analysis.
  - [:file\_folder: figures](manuscript/figures): Plots and other
    illustrations
  - [:file\_folder:
    videos](manuscript/videos):
    Videos.
  - [:file\_folder:
    source_data](/manuscript/source_data):
    Source data files associated with each figure containing all data points that have been plotted in the figure.
